
# Time-series data is often [non-stationary]{.underline}. {background-image="images/bg-aerial-view.jpeg"}

## So, what is [stationarity]{.underline}? {background-image="images/bg-aerial-view.jpeg" transition="none"}

> *A stationary time series is one whose statistical properties do not depend on the time at which the series is observed.* [^1]

[^1]: *Forecasting Principles and Practice, 3rd Edition*, Rob J. Hyndman and George Athansopoulos

:::: {.columns}
::: {.column width="50%"}
::: {.fragment}
```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.width: 6
#| fig.height: 5

ggplot(get_ts(start = Sys.Date()-45, end = Sys.Date() - 1,
              base = 20000, trend = 0.5), aes(x = date, y = value)) +
  geom_line(color = s_line_1, linewidth = 1.1) +
  labs(title = "Varying Mean") +
  scale_y_continuous(expand = c(0,0), limits = ~ c(0, max(.x) * 1.1), label = comma) +
  theme_main +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())

```
:::
:::
::: {.column width="50%"}
::: {.fragment}
```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.width: 6
#| fig.height: 5

ggplot(get_ts(start = Sys.Date()-45, end = Sys.Date() - 1,
              base = 20000, varying_variance = TRUE), aes(x = date, y = value)) +
  geom_line(color = s_line_1, linewidth = 1.1) +
  labs(title = "Varying Variance") +
  scale_y_continuous(expand = c(0,0), limits = ~ c(0, max(.x) * 1.1), label = comma) +
  theme_main +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
```
:::
:::
::::

## So, what is [stationarity]{.underline}? {background-image="images/bg-aerial-view.jpeg" transition="none"}

> *A stationary time series is one whose statistical properties do not depend on the time at which the series is observed.* [^1]

[^1]: *Forecasting Principles and Practice, 3rd Edition*, Rob J. Hyndman and George Athansopoulos

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.width: 12
#| fig.height: 4

ggplot(get_ts(start = Sys.Date()-60, end = Sys.Date() - 1,
              base = 20000), aes(x = date, y = value)) +
  geom_line(color = s_line_1, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(0, max(.x) * 1.1), label = comma) +
  theme_main +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
```

## So, what is [stationarity]{.underline}? {background-image="images/bg-aerial-view.jpeg" transition="none"}

> *A stationary time series is one whose statistical properties do not depend on the time at which the series is observed.* [^1]

[^1]: *Forecasting Principles and Practice, 3rd Edition*, Rob J. Hyndman and George Athansopoulos

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.width: 12
#| fig.height: 4

ggplot(get_ts(start = Sys.Date()-60, end = Sys.Date() - 1,
              base = 20000, week_season = TRUE), aes(x = date, y = value)) +
  geom_line(color = s_line_1, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(0, max(.x) * 1.1), label = comma) +
  theme_main +
  theme(axis.title.y = element_blank(),
        axis.text.y = element_blank())
```
