# Decomposition {background-color="#04447B7C"}

# [Time-Series]{.underline} Decomposition, That Is {background-color="#04447B7C"}

## Consider a fairly "clean" series {background-color="#04447B7C" transition="fade"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

df_trend_weekly_orig <- get_ts(start = Sys.Date() - 51, base = 10000, week_season = TRUE, trend = 0.8)

# This is just to not get caught up in weirdness in the explanation, but we're going to
# remove the first 3 and last 3 rows in the plots—for the trend calculation, these become
# NAs because it's a moving average.
df_trend_weekly <- df_trend_weekly_orig[4:(nrow(df_trend_weekly_orig) - 3),]

# Add the upper and lower bounds for geom_ribbon in next section
sd_tw <- sd(df_trend_weekly$value)
mean_tw <- mean(df_trend_weekly$value)
df_trend_weekly <- df_trend_weekly |> 
  mutate(u_bound_1 = mean_tw + sd_tw,
         l_bound_1 = if_else(mean_tw - sd_tw < 0, 0, mean_tw - sd_tw),
         u_bound_2 = mean_tw + 2*sd_tw,
         l_bound_2 = if_else(mean_tw - 2*sd_tw < 0, 0, mean_tw - 2*sd_tw))

gg_trend_weekly <- ggplot(df_trend_weekly, aes(x = date, y = value)) +
  geom_line(color = s_line_1, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(0, 22000), label = comma) +
  theme_main +
  theme(axis.title.y = element_blank())

gg_trend_weekly

```
## The Mean...is Pretty Meaningless {background-color="#04447B7C" transition="fade"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

gg_trend_weekly +
  geom_hline(aes(yintercept = mean_tw), linetype = "dashed", size = 3, color = "white") 

```
## And so is the variance {background-color="#04447B7C" transition="fade"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

gg_trend_weekly +
  geom_ribbon(aes(ymin = l_bound_2, ymax = u_bound_2), 
              fill = "yellow", alpha = 0.2) +
  geom_ribbon(aes(ymin = l_bound_1, ymax = u_bound_1), 
              fill = "red", alpha = 0.2) +
  geom_hline(aes(yintercept = mean_tw), linetype = "dashed", size = 3, color = "white")

```

# Time-series decomposition does what our brain already wants to do {background-color="#04447B7C"}

## The "decomposition" is into three components {background-color="#04447B7C" auto-animate="true"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

# Do the time-series decomposition. We're going to do this on the original
# data...and then the first and last 3 rows will get dropped.
ts_trend_weekly <- df_trend_weekly_orig |> 
  pull(value) |> 
  ts(frequency = 7) |> 
  decompose()

# Make it a data frame
df_decomposed <- tibble(date = df_trend_weekly_orig$date,
                        original = as.numeric(ts_trend_weekly$x),
                        seasonal = as.numeric(ts_trend_weekly$seasonal),
                        trend = as.numeric(ts_trend_weekly$trend),
                        random = as.numeric(ts_trend_weekly$random)) |> 
  # Chop off the first 3 / last 3 to avoid confusion
  filter(!is.na(trend))

# Set up some additional theming to make the "short" plots work
theme_stl <- theme(axis.text.x = element_blank(),
                   axis.title.y = element_blank(),
                   axis.text.y = element_text(size = s_axis_text_size * .75),
                   axis.line.x = element_blank())

gg_trend_weekly

```

## The "decomposition" is into three components {background-color="#04447B7C" auto-animate="true"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.height: 1.3

gg_stl_observed <- gg_trend_weekly +
  theme_stl

gg_stl_observed

```

. . .

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.height: 1.3

gg_stl_seasonal <- ggplot(df_decomposed, aes(x = date, y = seasonal)) +
  geom_hline(aes(yintercept = 0), color = "white") +
  geom_line(color = s_line_2, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(min(.x) * 1.1, max(.x) * 1.1), label = comma) +
  theme_main +
  theme_stl

gg_stl_seasonal

```
::: {.absolute top="250" left="280" .h2-chars}
The Seasonal Component
:::
. . .

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.height: 1.3

gg_stl_trend <- ggplot(df_decomposed, aes(x = date, y = trend)) +
  geom_hline(aes(yintercept = 0), color = "white") +
  geom_line(color = s_line_2, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(min(.x) * 1.1, max(.x) * 1.1), label = comma) +
  theme_main +
  theme_stl

gg_stl_trend

```

::: {.absolute top="400" left="310" .h2-chars}
The Trend Component
:::
. . .

```{r}
#| dev.args: !expr 'list(bg="transparent")'
#| fig.height: 1.3

gg_stl_random <- ggplot(df_decomposed, aes(x = date, y = random)) +
  geom_hline(aes(yintercept = 0), color = "white") +
  geom_line(color = s_line_2, linewidth = 1.1) +
  scale_y_continuous(expand = c(0,0), limits = ~ c(min(.x) * 1.1, max(.x) * 1.1), label = comma) +
  theme_main +
  theme_stl

gg_stl_random

```

::: {.absolute top="550" left="370" .h2-chars}
What's Left!
:::

## Our original mean and variance now seems...embarrassing? {background-color="#04447B7C"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

gg_trend_weekly +
  geom_ribbon(aes(ymin = l_bound_2, ymax = u_bound_2), 
              fill = "yellow", alpha = 0.2) +
  geom_ribbon(aes(ymin = l_bound_1, ymax = u_bound_1), 
              fill = "red", alpha = 0.2) +
  geom_hline(aes(yintercept = mean_tw), linetype = "dashed", size = 3, color = "white")

```

## We can use the seasonal and trend components for the "mean" {background-color="#04447B7C"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

# Get the sd of the random
random_sd <- sd(df_decomposed$random, na.rm = TRUE)

df_trend_weekly_final <- df_decomposed |> 
  # Calculate the "mean" by adding the seasonal and trend
  mutate(mean = seasonal + trend) |> 
  # Add in upper and lower bounds
  mutate(bound_u = mean + 2 * random_sd,
         bound_l = mean - 2 * random_sd)

gg_trend_weekly +
  geom_line(mapping = aes(x = date, y = mean), data = df_trend_weekly_final, 
            color = "white", linetype = "dashed", size = 2)

```

## And the "variance" is [just]{.underline} based on "what's left" {background-color="#04447B7C"}

```{r}
#| dev.args: !expr 'list(bg="transparent")'

gg_trend_weekly +
  geom_ribbon(mapping = aes(x = date, y = 0, ymin = bound_l, ymax = bound_u), 
              data = df_trend_weekly_final, fill = "yellow", alpha = 0.2) +
  geom_line(mapping = aes(x = date, y = mean), data = df_trend_weekly_final, 
            color = "white", linetype = "dashed", size = 2)


```


# This is powerful! {background-color="#04447B7C"}

# (Loosely) it's part of what's happening with our next example. {background-color="#04447B7C"}

